---
title: "Lab Week 8"
author: "Donald Elrod"
date: "May 10, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1
```{r}
th = (1:37)/40
p.th = sqrt( (40*th-1)/36)
th.hat.3=th.hat.2=MSE3=MSE2=0
for (i in 1:37) {
  for (j in 1:5000) {
    pop = rep(c(p.th[i], 0.5), c(9,1))
    random.p = sample(pop, size=100, replace=T)
    samp = rbinom(100, 2, random.p)
    p.3 = (mean(samp)-0.1)/1.8;
    p.3 = min( max(0, p.3), 1)
    th.hat.3[j] = (36*p.3^2 + 1)/40;
    th.hat.2[j] = mean(samp==2)
  }
  mth3 = (th.hat.3 - th[i])^2
  mth2 = (th.hat.2 - th[i])^2
  MSE3[i] = mean(mth3)
  MSE2[i] = mean(mth2)
}

ymax = max(MSE3, MSE2)

plot(th, MSE3, col='blue', ylim=c(0, ymax), xlab = 'th', ylab = 'MSE values')
points(th, MSE2, col='red')
```
```{r}
summary(MSE2)
summary(MSE3)
```
# Question 2
$\theta_2$ seems a better fit for the data, as it seem more normally distributed than $\theta_3$, however $\theta_3$ is a better model in the range of ~ 0.6


# Question 3
```{r}
pop = rep(c(0.7, 0.5), c(9,1))
random.p = sample(pop, size=100, replace=T)
samp = rbinom(100, 2, random.p)
p = (1:49)/50

binom.mix.logL=function(p,data) {
  probdist=0.9*dbinom(data,2,p)+0.1*dbinom(data,2,0.5)
  sum(log(probdist))
}

logL=0

for(i in 1:49){
  logL[i]=binom.mix.logL(p[i],samp)
}

plot(p, logL, type='l')


```


# Question 4
```{r}
fit = optimise(binom.mix.logL, c(0,1), data=samp, maximum=T)
fit$max
```

# Question 5
```{r}
th = (1:37)/40
p.th = sqrt( (40*th-1)/36)
th.hat.4=MSE4=0
for (i in 1:37) {
  for (j in 1:5000) {
    pop = rep(c(p.th[i], 0.5), c(9,1))
    random.p = sample(pop, size=100, replace=T)
    samp = rbinom(100, 2, random.p)
    p.4 = optimise(binom.mix.logL, c(0,1), data=samp,maximum=T)$max
    th.hat.4[j] = (36*p.4^2 + 1)/40;
  }
  mth4 = (th.hat.4 - th[i])^2
  MSE4[i] = mean(mth4)
}
```


```{r}

ymax = max(MSE2, MSE3, MSE4)

plot(th, MSE4, col='blue', ylim=c(0, ymax), xlab = 'th', ylab = 'MSE values')
points(th, MSE2, col='red')
points(th, MSE3, col='green')
```

# Question 6
$\theta_2$ seems to have a better fit for the simulation when the range is ~0.5, whereas $\theta_3$ and $\theta_4$ appear to be more accurate in the range of ~0.6-7, with $\theta_3$ being closer to 0.7 and $\theta_4$ being closer to 0.6
